### 2022-05-05 manuscript.Rmd
Move manuscript and supplement to root dir

bibliography      : "references.bib"
csl               : "nature.csl"

@@

# Supplementary information

```{r, tabs1, include=TRUE}
# Save within-analysis table of experiments
dat %>%
  mutate(
    age_mean = format_days_months(age_mean),
    age_sd = str_c(as.character(round(age_sd)), "d"),
  ) %>%
  transmute(
    Article = if_else(article == lag(article, default = ""), "", article),
    Experiment = group_long,
    `Sample size` = sample_size,
    `Females` = round(female_percent * sample_size),
    Age = str_c(age_mean, "±", age_sd, sep = " "),
    Task = task,
    `Stimulus type` = str_to_sentence(stimuli_presentation),
    `Stimulus dimensions` = stimuli_dimensions
  ) -> tabs1

# Save the table
write_csv(tabs1, file = here(tables_dir, "within_experiments.csv"), na = "n/a")

# Display the table
apa_table(
  tabs1,
  caption = "Experiments included in the main analysis", label = "S1",
  landscape = TRUE, font_size = "scriptsize"
)
```

```{r, figs1, include=TRUE, fig.height=10, fig.width=12, fig.cap="(ref:figs1-caption)"}
# Get posterior draws for the effect in each experiment
epred_draws_brm_gender <- epred_draws(res_brm_gender, dat_gender, ndraws = NULL) %>%
  mutate(experiment_f = factor(experiment))

# Create forest plot
dat_gender %>%
  # Make sure the plot will be ordered alphabetically by experiment IDs
  arrange(experiment) %>%
  mutate(
    experiment_f = fct_rev(fct_expand(factor(experiment), "model")),
    # Show article labels only for the first experiment per article
    article = if_else(article == lag(article, default = ""), "", article),
    # Compute frequentist confidence intervals
    ci_lb = gi - qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
    ci_ub = gi + qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
    ci_print = print_ci(gi, ci_lb, ci_ub)
  ) %>%
  # Prepare plotting canvas
  ggplot(aes(x = gi, y = experiment_f)) +
  geom_vline(xintercept = seq(-3, 3, 0.5), color = "grey90") +
  # Add article and group labels as text on the left
  geom_text(aes(x = -9.9, label = article), hjust = 0) +
  geom_text(aes(x = -7.1, label = group_long), hjust = 0) +
  # Add experiment-specific effect sizes and CIs as text on the right
  geom_text(aes(x = 3.7, label = print_num(gi)), hjust = 1) +
  geom_text(aes(x = 4.4, label = print_num(ci_lb)), hjust = 1) +
  geom_text(aes(x = 5.1, label = print_num(ci_ub)), hjust = 1) +
  # Add Bayesian highest posterior density intervals for each experiment
  stat_interval(
    aes(x = .epred),
    data = epred_draws_brm_gender,
    alpha = .8,
    point_interval = "mean_qi",
    .width = c(0.5, 0.95),
  ) +
  scale_color_grey(
    start = 0.85, end = 0.65,
    labels = as_mapper(~ scales::percent(as.numeric(.x)))
  ) +
  # Add experiment-specific effect sizes and CIs as dots with error bars
  geom_linerange(aes(xmin = ci_lb, xmax = ci_ub), size = 0.35) +
  geom_point(aes(size = ni), shape = 22, fill = "white") + # Or (1 / vi)?
  # Add posterior distribution for the meta-analytic effect
  stat_halfeye(
    aes(x = intercept, y = -1),
    draws_brm_gender,
    point_interval = "mean_qi",
    .width = c(0.95)
  ) +
  annotate(
    "text",
    x = c(-9.9, 3.7, 4.4, 5.1),
    y = -0.5,
    label = c(
      "Three-level model",
      print_num(summ_brm_gender$intercept),
      print_num(summ_brm_gender$intercept.lower),
      print_num(summ_brm_gender$intercept.upper)
    ),
    hjust = c(0, 1, 1, 1),
    fontface = "bold"
  ) +
  # Add headers for each of the for columns
  annotate( # Just to make the grid lines disappear
    "rect",
    xmin = -Inf,
    xmax = Inf,
    ymin = nrow(dat_gender) + 0.5,
    ymax = Inf,
    fill = "white"
  ) +
  annotate(
    "text",
    x = c(-9.9, -7.1, 0, 3.7, 4.4, 5.1),
    y = nrow(dat_gender) + 1.5,
    label = c(
      "Article",
      "Experiment",
      "Effect size plot",
      "Effect size",
      "Lower",
      "Upper"
    ),
    hjust = c(0, 0, 0.5, 1, 1, 1),
    fontface = "bold"
  ) +
  # Styling
  coord_cartesian(
    ylim = c(-1.5, nrow(dat_gender) + 2), expand = FALSE, clip = "off"
  ) +
  scale_x_continuous(breaks = seq(-3, 3, 0.5)) +
  annotate("segment", x = -3.3, xend = 3.3, y = -1.5, yend = -1.5) +
  labs(
    x = expression("Hedges'" ~ italic("g")),
    size = "Sample size",
    color = "CrI level"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(family = "Helvetica", color = "black"),
    axis.text.y = element_blank(),
    axis.ticks.x = element_line(colour = "black"),
    axis.title.x = element_text(hjust = 0.67, margin = margin(b = -15)),
    axis.title.y = element_blank(),
    panel.grid = element_blank(),
    text = element_text(family = "Helvetica")
  )

# Save the plot
ggsave(here(figures_dir, "forest_gender.pdf"), width = 12, height = 8)
```

(ref:figs1-caption) **Meta-analysis of gender differences.** A Bayesian three-level meta-analysis provided evidence for a small gender difference in mental rotation performance between male and female infants. White squares indicate the effect sizes (Hedges’ $g$) for gender difference in all individual experiments and black lines their 95% confidence intervals. Note that for experiments that observed a non-significant gender difference and did not specify the exact size of this effect, we assumed an effect size of $g = 0.00$. Gray bars indicate the 95% and 50% Bayesian credible interval (CrI) based on a Bayesian three-level random-effects model. Note that these intervals got shrunk towards the meta-analytic effect size because of partial pooling, that is, the three-level model regularizing the impact of experiments with small sample sizes and/or unrealistically large effect sizes. The last line shows the meta-analytic effect size from the three-level model (black dot) together with its 95% CrI (black line) and its posterior distribution (gray curve).

```{r, figs2, include=TRUE, fig.height=6, fig.width=12, fig.cap="(ref:figs2-caption)"}
# Extract convergence statistics from results
conv_stats <- with(summary(res_brm), tibble(
  parameter = c(
    "b_Intercept", "sd_article__Intercept", "sd_article:experiment__Intercept"
  ),
  name_expr = c(
    "Hedges ~ italic(g)", "italic(sigma)[article]", "italic(sigma)[experiment]"
  ),
  r_hat = print_num(c(fixed$Rhat, map_dbl(random, ~ .$Rhat)), digits = 4),
  bulk_ess = round(c(fixed$Bulk_ESS, map_dbl(random, ~ .$Bulk_ESS))),
  tail_ess = round(c(fixed$Tail_ESS, map_dbl(random, ~ .$Tail_ESS))),
  r_hat_expr = str_c("italic(R)[hat] == ", r_hat),
  bulk_ess_expr = str_c("italic(N)[eff(bulk)] == ", bulk_ess),
  tail_ess_expr = str_c("italic(N)[eff(tail)] == ", tail_ess),
  y_pos = c(0.7, 0.75, 0.8)
))

# Create trace plot
n_draws <- n_iter - n_warmup
bayesplot::mcmc_trace(
  res_brm,
  pars = conv_stats$parameter, facet_args = list(ncol = 1)
) +
  geom_text(
    aes(y = 0.45, label = name_expr, color = NA),
    conv_stats,
    y = 0.45, x = -800, color = "black", parse = TRUE, angle = 90
  ) +
  geom_text(
    aes(y = y_pos, label = r_hat_expr, color = NA),
    conv_stats,
    x = 13000, hjust = 1, color = "black", parse = TRUE,
  ) +
  geom_text(
    aes(y = y_pos, label = bulk_ess_expr, color = NA),
    conv_stats,
    x = 16000, hjust = 1, color = "black", parse = TRUE,
  ) +
  geom_text(
    aes(y = y_pos, label = tail_ess_expr, color = NA),
    conv_stats,
    x = 19000, hjust = 1, color = "black", parse = TRUE,
  ) +
  labs(x = "Sample number", y = NULL, color = "MCMC\nchain") +
  coord_cartesian(expand = FALSE, clip = "off") +
  scale_x_continuous(limits = c(0, n_draws), breaks = seq(0, n_draws, 2000)) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_color_grey(start = 0.0, end = 0.9) +
  theme_classic() +
  theme(
    axis.line = element_line(colour = "black"),
    axis.text = element_text(family = "Helvetica", color = "black"),
    axis.ticks = element_line(color = "black"),
    plot.margin = margin(t = 10, l = 25),
    strip.background = element_blank(),
    strip.text = element_blank(),
    text = element_text(family = "Helvetica", color = "black")
  )

# Save the plot
ggsave(here(figures_dir, "trace.pdf"), width = 12, height = 6)
```

(ref:figs2-caption) Convergence checks.

```{r, frequentist_results}
# Three-level model
res_ml <- rma.mv(
  gi, vi,
  random = ~ 1 | article / experiment,
  data = dat,
  slab = experiment
)
print(res_ml)
# forest(res_ml)

# Check share of variance at each level of the model
round(res_ml$sigma2[1] / sum(res_ml$sigma2), 3) # Between-article (ICC)
round(res_ml$sigma2[2] / sum(res_ml$sigma2), 3) # Within-article (between-exp.)

# # Profile likelihodd plots for checking that REML has converged
# profile(res_ml)

# Meta-regression with gender, age, and task
res_reg <- rma.mv(
  gi, vi,
  mods = ~ gender * age_c + task,
  random = ~ 1 | article / experiment,
  data = dat,
  slab = experiment
)
print(res_reg)
# forest(res_full)

# Extract standard deviations and ICCs
vars_ml <- list(matrix())

# Export results as a table
map2_dfr(
  c("Meta-analysis", "Meta-regression"),
  list(res_ml, res_reg),
  function(name, res) {
    # Intercept / regression weights
    tibble(
      Model = c(name, rep(NA, length(res$b) - 1)),
      Parameter = rownames(res$b),
      Estimate = print_num(as.numeric(res$b)),
      SE = print_num(res$se),
      z = print_num(res$zval),
      p = print_num(res$pval, digits = 3),
      ci_lower = print_num(res$ci.lb),
      ci_upper = print_num(res$ci.ub)
    ) %>%
      # Re-format confidence interval
      mutate(
        `95% CI` = str_c("[", ci_lower, ", ", ci_upper, "]"),
        .keep = "unused"
      ) %>%
      # Add variances
      bind_rows(tibble(
        Parameter = res$s.name,
        Estimate = print_num(res$sigma2)
      ))
  }
) %>%
  mutate(
    Parameter = c(
      "Hedges' g",
      "s2article",
      "s2experiment",
      "Intercept",
      "Female - mixed",
      "Male - female",
      "Age (per year)",
      "Habituation - VoE",
      "(Female - mixed) × age",
      "(Male - female) × age",
      "s2article",
      "s2experiment"
    )
  ) -> tab_freq

# Save the table
write_csv(tab_freq, file = here(tables_dir, "frequentist_results.csv"), na = "")
```

```{r, sensitivity_analysis, eval=FALSE, include=TRUE}
# Compute empirical estimate of the correlation between dependent samples
dat %>%
  mutate(
    # Get effect size from paired samples t-test, one sample t-test, or ANOVA
    d_diff = case_when(
      !is.na(d) ~ d,
      !is.na(d_z_t) ~ d_z_t,
      !is.na(d_z_f) ~ d_z_f,
      !is.na(d_z_diff) ~ d_z_diff
    ),
    # Compute empirical correlation
    # Basesd on the SD of the difference and the SDs within the two conditions
    sd_diff = mean_diff / d_diff,
    ri = (sd_diff^2 - sd_novel^2 - sd_familiar^2) /
      (-2 * sd_novel * sd_familiar)
  ) %>%
  pull(ri) -> ri_empirical

# Summarise the estimated correlations
summary(ri_empirical)

# Re-run the meta-analysis for different values of r_assumed
seq(-0.9, 0.9, by = 0.3) %>%
  set_names(., str_c("r = ", print_num(.))) %>%
  map(function(ri_sens) {

    # Re-compute standard errors of the effect sizes
    mutate(
      dat,
      vi = (dfi / (dfi - 2)) * ((2 * (1 - ri_sens)) / ni) *
        (1 + gi^2 * (ni / (2 * (1 - ri_sens)))) - (gi^2 / ji^2),
      sei = sqrt(vi)
    ) -> dat_ri_sens

    # Re-run meta-analysis
    update(res_brm, newdata = dat_ri_sens, refresh = 0)
  }) -> res_ri_sens

# Prior sensitivity analysis
list(
  "Intercept U(-10,10)" = c(
    set_prior("uniform(-10, 10)", class = "Intercept"),
    set_prior("cauchy(0, 0.3)", class = "sd")
  ),
  "Intercept N(0,0.2)" = c(
    set_prior("normal(0, 0.2)", class = "Intercept"),
    set_prior("cauchy(0, 0.3)", class = "sd")
  ),
  "SD U(0,10)" = c(
    set_prior("normal(0, 1)", class = "Intercept"),
    set_prior("uniform(0, 10)", class = "sd")
  ),
  "SD Student-t(10,0,0.2)" = c(
    set_prior("normal(0, 1)", class = "Intercept"),
    set_prior("student_t(10, 0, 0.2)", class = "sd")
  )
) %>%
  # Re-run the meta-analysis with different priors
  map(
    function(prior_sens) update(res_brm, prior = prior_sens, refresh = 0)
  ) -> res_prior_sens

# Create a table summarizing all sensitivity analyses
map2_dfr(
  c(res_ri_sens, res_prior_sens),
  c(names(res_ri_sens), names(res_prior_sens)),
  function(res, name) {

    # Compute ICC
    var_experiment <- as.matrix(
      res,
      variable = "sd_article:experiment__Intercept"
    )^2
    var_article <- as.matrix(
      res,
      variable = "sd_article__Intercept"
    )^2
    var_total <- var_experiment + var_article
    icc <- var_article / var_total
    icc_row <- mean_qi(icc) %>%
      rename(Estimate = y, `l-95% CI` = ymin, `u-95% CI` = ymax)

    # Create a data frame row of summary statistics
    with(summary(res), bind_rows(fixed, bind_rows(random))) %>%
      bind_rows(icc_row) %>%
      transmute(
        parameter = c("Hedges' g", "SD_{article}", "SD_{experiment}", "ICC"),
        Estimate = print_ci(Estimate, `l-95% CI`, `u-95% CI`)
      ) %>%
      pivot_wider(names_from = parameter, values_from = Estimate) %>%
      bind_cols(Simulation = name, .)
  }
) -> tab_sens

# Save the table
write_csv(tab_sens, file = here(tables_dir, "sensitivity_analysis.csv"))
```

>>>>

bibliography      : "manuscript_files/references.bib"
csl               : "manuscript_files/nature.csl"

appendix          : "supplement.Rmd"

@@

```{r child = "supplement.Rmd"}
```
